Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-09-10 Docs/Paper/LaTex/template.tex
review 6 Related Work

Since the second half of the first decade of the 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, {\it i.e.}, to find the exact solution ~\cite{Mann2007}, to use heuristics to speed up performance time ~\cite{Arato2003}, and hybrid ones ~\cite{Arato2005}.

In the first group, the exact solution to the HW-SW partitioning problem is found. The use of SMT-based verification presented in this paper can be grouped into this category, because the exact solution is found with the given algorithm. The difference is based only in terms of the technique chosen to solve the problem.
Another path followed in past initiatives and which has had more studies is the creation of heuristics to speed up the running time of the solution. The difference between this kind of solutions and SMT-based verification is based on two facts: ESBMC is guaranteed to find the exact solution, but the heuristics are faster when the complexity is greater.

@@

In terms of SMT-based verification, most work is restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness. In ~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and ~\cite{Cordeiro2012} uses the ESBMC model checker for embedded ANSI-C software. In~\cite{Trindade2015} and~\cite{Trindade2014} it was proven that it is possible to use ESBMC to solve HW-SW partitioning, but in a single core way. There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification ~\cite{Holzmann2011}, and modifications of internal search engines to support parallelism ~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solvers ~\cite{Wintersteiger2009}. Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}.

$\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}. As an application example, Pavlinovic {\it et al.}~\cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion. The authors formulate this approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program. The approach described by Pavlinovic {\it et al.}, which uses MaxSMT solver $\nu$Z, shows a significant performance improvement if compared to previous SMT encodings and localization algorithms.

The problem addressed in this present paper uses a single objective function for minimization. In Partrick {\it et al.}~\cite{Patrick2015},  OptiMathSAT and $\nu$Z are compared for software optimization problems. OptiMathSAT using multiple objective functions works better than $\nu$Z; however, for problems with a single objective function, the performance of $\nu$Z is better than OptiMathSAT.

>>>>

Since the second half of the first decade of 2000s, three main paths have been tracked to improve or to present alternative solutions to the optimization of HW-SW partitioning, {\it i.e.}, to find the exact solution~\cite{Mann2007}, to use heuristics to speed up performance time~\cite{Arato2003}, and hybrid ones~\cite{Arato2005}.

In the first group, the exact solution to the HW-SW partitioning problem is found. The use of SMT-based verification presented in this paper can be grouped into this category, because the exact solution is found with the given algorithms. The difference is based only on the technique chosen to solve the problem.
Another path followed in past initiatives and which has had more studies is the creation of heuristics to speed up the running time of the solution. The difference of this kind of solution to SMT-based verification and maximum satisfiability is based on two facts: all ESBMC implementations guarantee to find the exact solution, but heuristics are faster, when the complexity is greater.

@@

In terms of SMT-based verification, most related studies are restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness. In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and~\cite{Cordeiro2012} uses ESBMC for embedded ANSI-C software. In~\cite{Trindade2015} and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way. There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification ~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism ~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solvers ~\cite{Wintersteiger2009}.

Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}. In particular, 
$\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}. As an application example, Pavlinovic {\it et al.}~\cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion. The authors formulate this approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program. The approach described by Pavlinovic {\it et al.}, which uses MaxSMT solver $\nu$Z, shows a significant performance improvement if compared to previous SMT encodings and localization algorithms.

The problem addressed in this present paper uses a single objective function for minimization. In Partrick {\it et al.}~\cite{Patrick2015},  OptiMathSAT and $\nu$Z are compared for software optimization problems. OptiMathSAT, using multiple objective functions, works better than $\nu$Z; however, for problems with a single objective function, the performance of $\nu$Z is better than OptiMathSAT.
